---
title: "MasterDatabase2"
author: "Akshay Jain"
date: "6/25/2019"
output: pdf_document
---
```{r}
library(fuzzyjoin)
library(lubridate)
library(dplyr)
```

#This is to create the master database using spreadsheets formed based off of the different race of the officers
#Import race spreadsheets and join them together 
```{r}
whites <- read.csv("../Datasets/Original Data/Complaint Subsets/WhiteOfficers.csv") %>% mutate(officerRace = "White")
blacks <- read.csv("../Datasets/Original Data/Complaint Subsets/BlackOfficers.csv") %>% mutate(officerRace = "Black")
hispanic <- read.csv("../Datasets/Original Data/Complaint Subsets/HispanicOfficers.csv") %>% mutate(officerRace = "Hispanic")
other <- read.csv("../Datasets/Original Data/Complaint Subsets/OtherRaceOfficers.csv") %>% mutate(officerRace = "Other")

MasterDatabase <-whites %>% rbind(blacks) %>% rbind(hispanic) %>% rbind(other) %>% rename(UID = OfficerID)
```

#Create officer field and a date field.
```{r}
MasterDatabase$officer <- paste(MasterDatabase$OfficeFirst, MasterDatabase$OfficerLast)
MasterDatabase$Date <- ymd_hms(MasterDatabase$IncidentDate)
```

#Create field for whether complaints are departmental or civilian issued
```{r}
officer <- read.csv("../Datasets/Original Data/Complaint Subsets/Officer Filed Complaints.csv")
civilian <- read.csv("../Datasets/Original Data/Complaint Subsets/CivilianFiledComplaints.csv")

MasterDatabase$Filedby <- ifelse(MasterDatabase$CRID %in% officer$CRID, "Officer Filed", ifelse(MasterDatabase$CRID %in% civilian$CRID, "Civilian Filed", "Unknown"))
```

#Fix up Roster Data
```{r}
proper=function(x) paste0(toupper(substr(x, 1, 1)), tolower(substring(x, 2)))

rosterNew <- read.csv("../Datasets/Original Data/Other_Raw_Data/roster__2018-03.csv")
rosterOld <- read.csv("../Datasets/Original Data/Other_Raw_Data/roster_1936-2017_2017-04.csv")

library(plyr)
megaRoster <- rbind.fill(rosterOld, rosterNew)  %>% distinct()
megaRoster <- megaRoster %>% filter(link_UID != -999) %>% arrange(link_UID)
detach(package:plyr)

library(dplyr)

megaRoster$UID <- ifelse(is.na(megaRoster$old_UID), megaRoster$link_UID, megaRoster$old_UID)
megaRoster$officer <- paste(proper(megaRoster$first_name), proper(megaRoster$last_name))
megaRoster <- megaRoster %>% select(officer, UID, middle_initial, gender, race, current_age, current_status, current_rank, appointed_date, resignation_date)
megaRoster <- megaRoster %>% distinct(UID, .keep_all = TRUE)

megaRoster %>% 
  mutate(startYear = ifelse(year(mdy(appointed_date)) >2020,year(mdy(appointed_date))-100, year(mdy(appointed_date))))%>%
  mutate(startYear = ifelse(is.na(startYear),  ifelse(year(ymd(appointed_date)) >2020,year(ymd(appointed_date))-100, year(ymd(appointed_date))),startYear)) %>% 
  mutate(resignation_date = ifelse(resignation_date =="", "01/01/2018", resignation_date)) %>% 
  mutate(endYear = ifelse(year(mdy(resignation_date)) >2020,year(mdy(resignation_date))-100, year(mdy(resignation_date)))) %>% 
  filter(!is.na(endYear))
endYears <- roster %>% filter(is.na(endYear)) %>% mutate(endYear = year(ymd(resignation_date)))
megaRoster <- megaRoster %>% 
  rbind(endYears) %>% 
  mutate(yearsOnForce = endYear - startYear) %>% 
  mutate(resignation_date = ifelse(resignation_date == "01/01/2018", NA, resignation_date)) %>% 
  mutate(endYear = ifelse(is.na(resignation_date), NA, endYear))
```


#This is a dataset of each officer and their UID
```{r}
officers<- MasterDatabase %>% select(officer, UID) %>% distinct()
megaRosterCopy <- megaRoster 
megaRosterCopy$UID <- megaRosterCopy$UID
megaRosterCopy <- megaRosterCopy %>% select(officer, UID) %>% distinct()

officers <- officers %>% rbind(megaRosterCopy) %>% distinct()
officers
```

#This cleans up unit history data
```{r}
unit_history <- read.csv("../Datasets/Original Data/Other_Raw_Data/unit-history.csv", stringsAsFactors = FALSE)
unit_history$officer <- officers$officer[match(unit_history$link_UID, officers$UID)]

unit_history$unit_start_date <- mdy(unit_history$unit_start_date)
unit_history$unit_end_date <- mdy(unit_history$unit_end_date)
unit_history$start_month <- month(unit_history$unit_start_date)
unit_history$start_day <- day(unit_history$unit_start_date)
unit_history$start_year <- year(unit_history$unit_start_date)
unit_history$start_year<- ifelse(unit_history$start_year>2019, unit_history$start_year-100, unit_history$start_year)
unit_history$start_date <- mdy(paste0(unit_history$start_month,"-", unit_history$start_day,"-", unit_history$start_year))

unit_history$end_month <- month(unit_history$unit_end_date)
unit_history$end_day <- day(unit_history$unit_end_date)
unit_history$end_year <- year(unit_history$unit_end_date)
unit_history$end_year<- ifelse(unit_history$end_year>2019, unit_history$end_year-100, unit_history$end_year)
unit_history$end_date <- mdy(paste0(unit_history$end_month,"-", unit_history$end_day,"-", unit_history$end_year))

unit_history <- unit_history %>% 
  select(officer, unit, link_UID, start_date, end_date) %>% 
  rename(UID = link_UID)
```

#This is the process that joins unit history and complaints.
```{r}
#Add unit assignments for all officers
FullData <- MasterDatabase %>% mutate(unit = 1) %>% filter(unit == -1) #Creates an empty dataframe with the correct columns
UIDS <- MasterDatabase %>% select(UID) %>% distinct() %>% arrange(UID) %>% pull(UID)
for(j in 1:length(UIDS)){
    i = UIDS[j]
    subsettedData <- MasterDatabase %>% filter(UID ==i)
    subsettedUnits <- unit_history %>% filter(UID == i )
    eachOfficer<- fuzzy_left_join(
     subsettedData, subsettedUnits,
      by = c(
        "UID"= "UID",
        "Date" = "start_date",
        "Date" = "end_date"
        ),
      match_fun = list(`==`, `>=`, `<=`)
      ) %>% select(-c(start_date, end_date))
    eachOfficer <- data.frame(eachOfficer)
    FullData <- FullData %>% rbind(eachOfficer)
    svMisc::progress(j,length(UIDS))
}
FullData

FullData$year <- year(FullData$Date)
```

#Get rid of the "C" that precedes some complaints
```{r}
Cs <- as.character((FullData %>% filter(grepl("C", CRID)))$CRID)

for(i in 1:length(Cs))
  Cs[i] = substr(Cs[i],2,10)

notCs <- as.character((FullData %>% filter(!grepl("C", CRID)))$CRID)
numericDups <- intersect(notCs, Cs)

cDups <- numericDups
for(i in 1:length(cDups))
{
  cDups[i] = paste0("C",cDups[i])
}

FullData <- FullData %>% filter(!CRID %in% cDups)
FullData$CRID <- as.character(FullData$CRID)

FullData <- FullData %>% mutate(CRID = ifelse(grepl("C", CRID), gsub("C", "", CRID), CRID))
```


#Adding field for complaints that involved officers in different units
```{r}
crossUnits <- FullData %>% 
  filter(!is.na(unit)) %>% 
  group_by(CRID) %>% 
  summarize(Result=n_distinct(unit)) %>% 
  filter(Result>1) %>% 
  pull(CRID)

FullData <- FullData %>% 
  mutate(crossUnit = ifelse(CRID %in% crossUnits, "Yes", "No"))
```

#Clean up some of the fields that were messed up from the previous steps
```{r}
FullData <- FullData %>% 
  rename(UID = UID.x) %>% 
  rename(officer = officer.x) %>% 
  select(-c(officer.y,UID.y))
```

#Obtain dataset of each complaint and how many officers were listed on a complaint
```{r}
offPerComp <- FullData %>% 
  count(CRID) %>% 
  as.data.frame() %>% 
  rename(no_of_officers = n)
```

#Obtain filtered master database that has only officers who have received more than one complaint. This will be used for network creation.
```{r}
md_moreThanOne <- FullData %>% 
  group_by(UID) %>% 
  filter(n()>1)
```

#Fix up settlement data so that UID is the correct UID that we've been using. 
#It looks like the current UID field matches up with the unit history UID field, so we join them and then rename fields. 
```{r}
uh <- read.csv("../Datasets/Original Data/Other_Raw_Data/unit-history.csv", stringsAsFactors = FALSE)
settlements <- read.csv("../Datasets/Original Data/settlements_1952-2016_2017-01.csv") %>% 
  mutate(year = as.numeric(substring(as.character(incident_date),1,4))) %>% filter(year>1989) %>% 
  left_join(uh, by = "UID") %>% 
  mutate(settlement = as.character(settlement)) %>%
  mutate(settlement = substr(settlement,2,nchar(settlement))) %>% 
  mutate(settlement = gsub(",", "",settlement)) %>%
  mutate(settlement = as.numeric(settlement)) %>% 
  select(-UID) %>% 
  rename(UID = link_UID) %>%
  left_join(officers, by = "UID") %>% 
  select(case_id, UID, officer, complaint, incident_date, location, plantiff, settlement, service_length, year) %>% 
  distinct() %>% 
  rename(plaintiff = plantiff) 
```

#Export all Data
```{r}
write.csv(FullData, "../Datasets/Complaint_Dataset.csv")
write.csv(megaRoster, "../Datasets/Final_Roster.csv")
write.csv(unit_history, "../Datasets/Final_Unit_History.csv")
write.csv(md_moreThanOne, "../Datasets/Complaints_MoreThanOneComplaint.csv")
write.csv(offPerComp, "../Datasets/OfficersPerComplaint.csv")
write.csv(settlements, "../Datasets/Settlements.csv")
```